Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update windows for wcrqa results for target filtering

For social cohesion and count of all events, there was a consistent period of
above-chance RR from the 7th--12th and 36th--47th window. In addition to some
one-week peaks at the beginning of the time period, DET was largely above chance
from the 46th to the 61st window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 20-30. DET was at or above chance for the 7th--17th, 32nd--34th, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

>>>>

For social cohesion and count of all events, there was a consistent period of
above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
one-week peaks at the beginning of the time period, DET was largely above chance
from the 46th to the 61st window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
